What We Eval in the Shadows

### 2021-04-14 paper/main.tex
Example about match.call and one argument evaluation

In \emph{MCMCglmm} (Monte Carl Markov Chain Generalised Linear Mixed Models), a \c{Dtensor} object is created, which contains expressions derived twice (with \c{DD}) and then typically in a list or a data frame.
\begin{lstlisting}
 expr<-expression(beta\_1 + time*beta\_2+u)
 ...
 mu = data.frame(beta\_1=0.5, beta\_2=1, time=3, u=2.3)
 ...
 D[i]<-eval(DD(expr, name[unlist(comb.pos[i,])]), mu)
\end{lstlisting}
% See https://github.com/cran/MCMCglmm/blob/cfac9e67ec73a3db2142826faae35e5d2318da31/man/evalDtensor.Rd

@@

A related pattern is not to change the call but rather to evaluate the arguments in the parent frame. This can also be achieved with \c{substitute}.
% Example

>>>>

In \emph{MCMCglmm} (Monte Carl Markov Chain Generalised Linear Mixed Models), a \c{Dtensor} object is created, which contains expressions derived twice (with \c{DD}) and then typically in a list or a data frame.
\begin{lstlisting}
 expr<-expression(beta_1 + time*beta_2+u)
 ...
 mu = data.frame(beta_1=0.5, beta_2=1, time=3, u=2.3)
 ...
 D[i]<-eval(DD(expr, name[unlist(comb.pos[i,])]), mu)
\end{lstlisting}
% See https://github.com/cran/MCMCglmm/blob/cfac9e67ec73a3db2142826faae35e5d2318da31/man/evalDtensor.Rd

@@

A related pattern is not to change the call but rather to evaluate the arguments in the parent frame. This could also be achieved with \c{substitute}, but \c{match.call} does it in bulk.
In package \emph{MedDietCalc},  in function \c{computeMDS95}, \c{match.call} retrieves the argument expressions of the call, which are evaluated in a dataframe \c{data} which contains the numeric data. Each argument of function \c{computeMDS95} is also a column in dataframe \c{data}. The advantage of using \c{eval} here is to be able to express an argument as a combination of several columns in the dataframe.
\begin{lstlisting}
computeMDS95 <- function (data, Vegetables, Legumes, FruitAndNuts, Cereals,
	 Potatoes = NULL, Meat, Dairy, 	Alcohol, Fats = NULL, MUFA = NULL,
	  SFA = NULL, Sex, men = "male", women = "female", 	frequency = NULL,
	  output = "percent", rm.na = FALSE) {

	arguments <- as.list( match.call())
	Vegetables <- eval(arguments$Vegetables, data)
	Legumes <- eval(arguments$Legumes, data)
	FruitAndNuts <- eval(arguments$FruitAndNuts, data)
	Cereals <- eval(arguments$Cereals, data)
	Potatoes <- eval(arguments$Potatoes, data)
	...
\end{lstlisting}
